---
execute:
  echo: false
  message: false
  warning: false
---

## Context

Imagine we are working for a commercial real estate company and trying to organize our data to solve two problems

- we want to keep in contact with potential future sellers, we have a list of properties and their owners, but lots of the properties are officially own by a LLC entity lacking of a real person to contact.

- If a buyer visits our website, we want to have a recommendation system that suggests similar properties to the one he is looking at.



## Data

This project uses public data from [NYC Open Data](https://opendata.cityofnewyork.us/) with a limited focus on properties in Manhattan.

- [Tax Assessment](https://data.cityofnewyork.us/City-Government/Property-Valuation-and-Assessment-Data-Tax-Classes/8y4t-faws): assessments for purpose to calculate Property Tax. NYC organizes tax lots using the BOROUGH-BLOCK-LOT (BBL) system, where BOROUGH is a 1 digit number (BOROUGH = 1 is Manhattan), BLOCK is 5 digits, and LOT is 4 digits. BBL is used as a the unique property identifier across all 3 datasests. For example, the Empire State Building is in Manhattan (borough = 1), block is 835 (zero-padded to 00835), and lot is 0041 (zero-padded to 0041), giving a BBL of 1008350041.

  ```{r}
  vroom::vroom("data/tax_small_final.csv") |>
    dplyr::mutate(bbl = as.character(bbl)) |>
    dplyr::glimpse()
  ```

- [Deeds](https://data.cityofnewyork.us/City-Government/ACRIS-Real-Property-Master/bnx9-e6tj): legal documents produced during the transfer of real estate from one party to another

  ```{r}
  vroom::vroom("data/deed_small_final.csv") |>
    dplyr::mutate(bbl = as.character(bbl), deed_id = as.character(deed_id)) |>
    dplyr::glimpse()
  ```

- [Building Permits](https://data.cityofnewyork.us/Housing-Development/DOB-Permit-Issuance/ipu4-2q9a): approved building permits that allow the property owner to make structural changes (e.g. add a window, install a new plumbing system, etc).

  ```{r}
  vroom::vroom("data/permit_small_final.csv") |>
    dplyr::mutate(bbl = as.character(bbl), permit_owner_phone = as.character(permit_owner_phone)) |>
    dplyr::glimpse()
  ```


